---
title: "Predictive Maintenance"
author: "Reza Dwi Utomo"
date: "3/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Background

The trend of Industry 4.0 spreads drastically. Data abundance and rapid ICT (Information and Communication Technology), especially AI (Artificial Intelligence), development become a key factor to such next generation industry. Many industrial stakeholders compete to implement it. IoT (Internet of Things) and Big Data are some of its implementation. In general, IoT technology is used to collect the data plentifully and rapidly, in real time. Meanwhile, such fresh data in a huge amount will be analysed afterwards for prediction.

**Industri mana saja yang menggunakan pred maint dan tulis problem**
There is a lot of sectors which can apply such technology. They are, for example, manufacturing, mining, oil & gas, public transport, aviation, food & beverage, and power & energy. Their issues to be solved by Industry 4.0 basically are similar to each other. They have to manage their assets by increasing assets lives, lowering the costs, and avoiding any undesired and dangerous failure. The manufacturing industries have to maintain their machines to prevent any unwanted downtimes in order to reduce costs. The mining and oil & gas industries have to keep their assets in prime condition by maintaining them in efficient strategy. Since their activities in the field are exceptionally risky, any undesired failure is untolerable. In the public transport and aviation industries, they have to maintain their fleets effectively, economically, and safely, in order to provide proper services for their passengers. The food & beverage industries need the environment for their food and drink stable and controlled. This can be achieved by maintaining their equipment properly. Last but not least, for the power & energy industries, they have to, for example, maintain and protect their power plants, line distributions, and substations in order to provide reliable electricity service to their customers while decreasing costs and risks.

In industrial sector, one of the applications of Industry 4.0 can be found in so-called Predictive Maintenance. This brand-new type of maintenance benefits from IoT and Big Data to perform maintenance. It completely differs from its predecessors, i.e. corrective and preventive maintenances. Both traditional techniques emphasize human-based and manual investigation on machine conditions. Eventhough they are still important in some aspects, industry players are not recommended to leave their product maintenance alone with both techniques. For example, you could perform run-to-failure for your uncritical equipment; you might not need this predictive maintenance method. Even the uncritical equipment simply does not need preventive maintenance. However, you could not think the same for your critical equipment where any failure is totally untolerated for any condition. The old-school preventive maintenance might suggest you to create a maintenance schedule in order to carry out maintenance periodically. It was expected you could perform maintentance in correct moments to minimize any undesired failure. Nevertheless, what actually happened were, for example, more cost upfront, over maintenance, labor intensive, unpredictability, and many more. On the other hand, Predictive Maintenance comes to offer a new approach to overcome those drawbacks. Based on the advantages of IoT and Big Data technology, some of predictive maintenance applications are remaining useful life (RUL) prediction, failure classification, and image-based defect detection.

The RUL prediction lets you to predict what time cycle left before the equipment going to fail. This, consequently, will maximize your equipment performance until its real capacity before failure where in turn your cost also will be minimized. Subsequently, failure classification provides you the easiness to categorize the failure modes based on their characteristics. This will aid you to provide different maintenance treatments for dissimilar failure modes. Therefore, it is unnecessary to allocate profuse man powers, tools, and treatments for each failure mode. Afterwards, for image-based defect detection, you could easily detect any defect on your products. This will significantly reduce the operator's human-error when he ran the manual visual inspection. By applying this technique, even you could execute quality control inspection autonomously, quickly, and plentifully. This will help you to identify the suppliers with frequent defect supply. Thus, once again, you could maximize outputs while minimizing cost.

*tulis singkat metode yang digunakannya dan kaitannya dengan variabel yang tersedia*
The RUL prediction requires numeric analytics since it outputs a numeric result of remaining time of the analysed machine. Such result is acquired from the predictive analytics on the data available, i.e. sensor data. The data are fed into the machine learning model in order to *train* the model so that such model will be able to predict the future RULs. The machine learning approach of supervised learning is used in this RUL case as the model is *supervised* by the available data. Additionally, as the RUL prediction outputs numeric results, the regression type of supervised learning is used. Subsequently, for the failure classification, the outputs will be in categorical results, such as the categories of the failures. Failures' characteristics are used to cluster the failure categories. The machine learning approach for this case is clustering of unsupervised learning. Unlike supervised learning, unsupervised learning needs no data for training. It learns by itself. Finally, the image-based defect detection is based on classification technique. Like regression technique, classification also comes from supervised learning. Therefore, it requires the data available as training data. What makes classification different from regression is that classification outputs categorical results instead of numeric results. In this case, the classification technique is required to output categorical results (whether defect exists or does not) from pictures.

In this article, the aforementioned three applications of predictive maintenance are going to be discussed. As case studies and due to the lack of datasets, unsimilar datasets are going to be used for each application. The datasets are the following:

1. dataset candidates: [NASA Turbofan Engine](https://ti.arc.nasa.gov/tech/dash/groups/pcoe/prognostic-data-repository/#turbofan), [IEEE PHM 2012 Data Challenge Dataset](https://github.com/Lucky-Loek/ieee-phm-2012-data-challenge-dataset), or [Scania dataset](https://www.kaggle.com/uciml/aps-failure-at-scania-trucks-data-set) > for Remaining Useful Life (Regression)

2. dataset candidates: [Amruthnath dataset](https://github.com/nagdevAmruthnath/Predictive-Maintenance) or [Faulty Steel Plates UCI dataset](https://www.kaggle.com/uciml/faulty-steel-plates) > for failure classification (Unsupervised Learning)

3. Steel Defect Detection dataset (acquired from [Kaggle](https://www.kaggle.com/c/severstal-steel-defect-detection/overview)) is used for image-recognition based defect detection

The methods used for each application are regression, unsupervised learning, and image classification, respectively.

# Exploratory Data Analysis

```{r message=FALSE}
library(tidyverse)
library(lubridate)
```


```{r}
acc_names <- list.files("B:/Projects/ieee-phm-2012-data-challenge-dataset/Learning_set/Bearing1_1", pattern = "^acc")
files <- data.frame("hour" = 0, "minute" = 0, "second" = 0, "mu_second" = 0, "hor_acc" = 0, "ver_acc" = 0)
for (i in acc_names) {
    file1 <- read.csv(paste0("B:/Projects/ieee-phm-2012-data-challenge-dataset/Learning_set/Bearing1_1/", i))
    colnames(file1) <- c("hour", "minute", "second", "mu_second", "hor_acc", "ver_acc")
    files <- rbind(files, file1)
}
files
```

1) unit number
2) time, in cycles
3) operational setting 1
4) operational setting 2
5) operational setting 3
6) sensor measurement  1
7) sensor measurement  2
...
26)	sensor measurement  26

```{r}
train1 <- read.csv("data/train_FD001.txt", header = F, sep = " ") %>% select(-c("V27","V28"))
train2 <- read.csv("data/train_FD002.txt", header = F, sep = " ") %>% select(-c("V27","V28"))
train3 <- read.csv("data/train_FD003.txt", header = F, sep = " ") %>% select(-c("V27","V28"))
train4 <- read.csv("data/train_FD004.txt", header = F, sep = " ") %>% select(-c("V27","V28"))

colnames(train1) <- c("unit","time","opr_set1","opr_set2","opr_set3",paste0("sensor",1:21))
colnames(train2) <- c("unit","time","opr_set1","opr_set2","opr_set3",paste0("sensor",1:21))
colnames(train3) <- c("unit","time","opr_set1","opr_set2","opr_set3",paste0("sensor",1:21))
colnames(train4) <- c("unit","time","opr_set1","opr_set2","opr_set3",paste0("sensor",1:21))
```

```{r}
trains <- list(train1,train2,train3,train4)
for (i in 1:length(trains)) {
    print(anyNA(trains[[i]]))
}
# rm(trains)
```

```{r}
for (i in 1:length(trains)) {
    str(trains[[i]])
}
```

```{r}

```

```{r}

```

```{r}
addr <- list.files("B:/Projects/Predictive-Maintenance/Remaining Useful Life")
coba <- read.csv(paste0("B:/Projects/Predictive-Maintenance/Remaining Useful Life/", addr))
coba
plot(coba$time, coba$health)
```

